---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fishwork

<!-- badges: start -->
<!-- badges: end -->

The purpose of working with the fishwork package is to make it easier for you, first of all, to develop various applications.

Here are collected functions that have to be dragged from project to project, so I decided to collect them in one package.

I hope that over time, the number of functions will increase.

## Installation

Over time, instructions will appear here.

```{r,eval = FALSE}
devtools::install_github("stwand/fishwork")
```

## Example

Examples are not everywhere. I know how to use it, third-party use does not bother me yet, and I'm not sure that anyone but me will need it.

## Quotes and Acknowledgments

I am happy to attach quotes for the packages used in the work.

**base** 

R Core Team (2023). R: A language and environment for statistical
  computing. R Foundation for Statistical Computing, Vienna, Austria. URL
  https://www.R-project.org/.

**checkmate**

Lang M (2017). “checkmate: Fast Argument Checks for Defensive R
  Programming.” _The R Journal_, *9*(1), 437-445.
  doi:10.32614/RJ-2017-028 <https://doi.org/10.32614/RJ-2017-028>.

**data.table**

Dowle M, Srinivasan A (2023). _data.table: Extension of `data.frame`_.
  https://r-datatable.com, https://Rdatatable.gitlab.io/data.table,
  https://github.com/Rdatatable/data.table.

**DBI**

R Special Interest Group on Databases (R-SIG-DB), Wickham H, Müller K
  (2022). _DBI: R Database Interface_. R package version 1.1.3,
  <https://CRAN.R-project.org/package=DBI>.

**futile.logger**

 Rowe BLY (2016). _futile.logger: A Logging Utility for R_. R package
  version 1.4.3, <https://CRAN.R-project.org/package=futile.logger>.

**glue**

Hester J, Bryan J (2022). _glue: Interpreted String Literals_. R
  package version 1.6.2, <https://CRAN.R-project.org/package=glue>.

**lubridate**

Garrett Grolemund, Hadley Wickham (2011). Dates and Times Made Easy
  with lubridate. Journal of Statistical Software, 40(3), 1-25. URL
  https://www.jstatsoft.org/v40/i03/.

**readr**

Wickham H, Hester J, Bryan J (2023). _readr: Read Rectangular Text
  Data_. R package version 2.1.4,
  <https://CRAN.R-project.org/package=readr>.

**this.path**

Simmons I (2023). _this.path: Get Executing Script's Path_. R package
  version 2.0.0, <https://CRAN.R-project.org/package=this.path>.

**qs**

Ching T (2023). _qs: Quick Serialization of R Objects_. R package
  version 0.25.5, <https://CRAN.R-project.org/package=qs>.

**Without these packages, R would not be as good as it is today.**

The book [R Packages (2e)](https://www.edwardtufte.com/tufte/books_be) was very helpful in creating this package.

